RIScatter: Unifying Backscatter Communication and Reconfigurable Intelligent Surface

### 2022-12-16 main.tex
:bento: Update simulation results

		\begin{algorithm}[!t]
			\caption{Numerical \gls{kkt} Input Distribution Evaluation by Limits of Sequence}
			\label{al:input_distribution}
			\begin{algorithmic}[1]
				\Require $K$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\varepsilon$
				\Ensure $\{\boldsymbol{p}_k^\star\}_{k \in \mathcal{K}}$
				\State Set $\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
				\State \phantom{Set} $\sigma^2_{m_{\mathcal{K}}}$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
				\State \phantom{Set} $f(z|\mathcal{H}_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
				\State \phantom{Set} $P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dmtmac}
				\State Initialize $r \gets 0$
				\State \phantom{Initialize} $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$
				\State Get $P_{\mathcal{K}}^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution} \label{st:input_distribution_begin}
				\State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
				\State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information} \label{st:input_distribution_end}
				\Repeat
					\State Update $r \gets r+1$
					\State \phantom{Update} $\boldsymbol{p}_k^{(r)}$, $\forall k$ by \eqref{eq:input_kkt_solution}
					\State Redo step \ref{st:input_distribution_begin}--\ref{st:input_distribution_end}
				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \varepsilon$
			\end{algorithmic}
		\end{algorithm}
	\end{subsection}

@@

				\Require $Q$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\varepsilon$

@@

				\Until $\lVert\boldsymbol{w}^{(r)}-\boldsymbol{w}^{(r-1)}\rVert \le \varepsilon$

@@

\begin{section}{Simulation Results}
	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision designs for the RIScatter system in Fig.~\ref{fg:riscatter_network}.
	We assume the AP-user distance is \qty{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
	% The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$.
	The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma,
	\end{equation}
	together with a Rician fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\varepsilon$, and we choose $b=9$ and $\varepsilon=\num{e-3}$.
	All achievable rate points/regions are averaged over \num{1000} channel realizations.

@@

				I_{\text{B}}(x_{\mathcal{K}};\hat{y}_{\text{\gls{sr}}}) = K \log M - \frac{\epsilon}{M^K},

@@

			where $\epsilon \triangleq \sum_{m_{\mathcal{K}}} \mathbb{E}_{\hat{v}} \log \sum_{m_{\mathcal{K}}'} \exp ( - {\lvert x_{m_{\mathcal{K}}} - x_{m_{\mathcal{K}}'} + \hat{v} \rvert^2}/{2 \sigma^2} )$ and $\hat{v} \sim \mathcal{CN}(0,\sigma_v^2/N)$.
			% For a sufficiently large $N$, $\epsilon$ is negligible and the total backscatter rate approaches $K \log M$.

@@

		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those applications.
		\emph{First,} we observe both \gls{bbc} and \gls{sr} almost ensure noise-free backscatter transmission when $N$ is sufficiently large.
		For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmtmac} \eqref{eq:dmtmac} becomes more reliable.
		For \gls{sr} with \gls{sic} and \gls{mrc}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\epsilon$ becomes insignificant.
		Such an \gls{sr} only guarantees the primary benefit with a large $N$, but decreases the backscatter symbol rate by a factor of $N$ and requires $N$ \gls{sic} processes to decode each backscatter symbol (tuple).
		\emph{Second,} the average primary rate slightly increases/decreases in the presence of a \gls{ambc}/\gls{ris} node, and the multipath benefit of \gls{sr} is unobvious.
		This is because the cascaded channel can be orders of magnitude weaker than the direct channel due to the double fading effect.
		\gls{ris} always ensures constructive superposition of direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that stochastically enhances the average primary rate.
		When $N$ is moderate, the randomly scattered signals should be modelled as primary interference rather than multipath components, and the \gls{sr} point will move towards the \gls{ambc} point.
		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff by smart input distribution design.
		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others by deterministic reflection pattern (no need for backscatter detection).
		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is higher than \gls{ambc} but lower than \gls{bbc} and \gls{sr}.
		This is because both RIScatter and \gls{ambc} employ semi-coherent (instead of coherent) energy detection in the presence of primary uncertainty, and RIScatter with adaptive channel coding can achieve higher backscatter rate than \gls{ambc} with equiprobable inputs.
		Importantly, such a practical RIScatter detection is feasible for arbitrary $N$, and using a fast-switching node with smaller $N$ can increase the backscatter throughput per unit time while preserving the dynamic passive beamforming gain on the primary link.
	\end{subsection}

>>>>

		\begin{algorithm}[!t]
			\caption{Numerical \gls{kkt} Input Distribution Evaluation by Limits of Sequence}
			\label{al:input_distribution}
			\begin{algorithmic}[1]
				\Require $K$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $\sigma_v^2$, $\rho$, $\boldsymbol{w}$, $\boldsymbol{t}$, $\epsilon$
				\Ensure $\{\boldsymbol{p}_k^\star\}_{k \in \mathcal{K}}$
				\State Set $\boldsymbol{h}_{\text{E}}^\mathsf{H}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_channel}
				\State \phantom{Set} $\sigma^2_{m_{\mathcal{K}}}$, $\forall m_{\mathcal{K}}$ by \eqref{eq:receive_variance}
				\State \phantom{Set} $f(z|\mathcal{H}_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:energy_distribution}
				\State \phantom{Set} $P(\hat{x}_{m_{\mathcal{K}}'}|x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}, m_{\mathcal{K}}'$ by \eqref{eq:dmtmac}
				\State Initialize $r \gets 0$
				\State \phantom{Initialize} $\boldsymbol{p}_k^{(0)} > \boldsymbol{0}$, $\forall k$
				\State Get $P_{\mathcal{K}}^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:equivalent_distribution} \label{st:input_distribution_begin}
				\State \phantom{Get} $I^{(r)}(x_{m_{\mathcal{K}}})$, $\forall m_{\mathcal{K}}$ by \eqref{eq:backscatter_information_function}, \eqref{eq:primary_information_function}, \eqref{eq:weighted_sum_information_function}
				\State \phantom{Get} $I^{(r)}_k(x_{m_k})$, $\forall k,m_k$ by \eqref{eq:backscatter_marginal_information}, \eqref{eq:primary_marginal_information}, \eqref{eq:weighted_sum_marginal_information}
				\State \phantom{Get} $I^{(r)}(x_{\mathcal{K}})$ by \eqref{eq:backscatter_mutual_information}, \eqref{eq:primary_mutual_information}, \eqref{eq:weighted_sum_mutual_information} \label{st:input_distribution_end}
				\Repeat
					\State Update $r \gets r+1$
					\State \phantom{Update} $\boldsymbol{p}_k^{(r)}$, $\forall k$ by \eqref{eq:input_kkt_solution}
					\State Redo step \ref{st:input_distribution_begin}--\ref{st:input_distribution_end}
				\Until $I^{(r)}(x_{\mathcal{K}}) - I^{(r-1)}(x_{\mathcal{K}}) \le \epsilon$
			\end{algorithmic}
		\end{algorithm}
	\end{subsection}

@@

				\Require $Q$, $N$, $\boldsymbol{h}_{\text{D}}^\mathsf{H}$, $\boldsymbol{H}_{\text{C}}$, $\boldsymbol{\alpha}$, $\mathcal{X}$, $P$, $\sigma_v^2$, $\rho$, $\{\boldsymbol{p}_k\}_{k \in \mathcal{K}}$, $\boldsymbol{t}$, $\alpha$, $\beta$, $\gamma$, $\epsilon$

@@

				\Until $\lVert\boldsymbol{w}^{(r)}-\boldsymbol{w}^{(r-1)}\rVert \le \epsilon$

@@

\begin{section}{Simulation Results}
	In this section, we provide numerical results to evaluate the proposed input distribution, active beamforming, and backscatter decision designs for the RIScatter system in Fig.~\ref{fg:riscatter_network}.
	We assume the AP-user distance is \qty{10}{\meter} and at least one RIScatter nodes are randomly dropped in a disk centered at the user with radius $r$.
	% The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$, all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$, and the user is with average noise power $\sigma_v^2=\qty{-40}{\dBm}$.
	The \gls{ap} is with an average transmit power budget $P=\qty{36}{\dBm}$ and all nodes employs $M$-\gls{qam} with amplitude scattering ratio $\alpha=0.5$.
	For all channels involved, we consider a distance-dependent path loss model
	\begin{equation}
		L(d) = L_0 \biggl(\frac{d_0}{d}\biggr)^\gamma,
	\end{equation}
	together with a Rician fading model
	\begin{equation}
		\boldsymbol{H} = \sqrt{\frac{\kappa}{1+\kappa}} \bar{\boldsymbol{H}} + \sqrt{\frac{1}{1+\kappa}} \tilde{\boldsymbol{H}},
	\end{equation}
	where $d$ is the transmission distance, $L_0=-\qty{30}{\dB}$ is the reference path loss at $d_0=\qty{1}{\meter}$, $\kappa$ is the Rician $K$-factor, $\bar{\boldsymbol{H}}$ is the deterministic line-of-sight component with unit-magnitude entries, and $\tilde{\boldsymbol{H}}$ is the Rayleigh fading component with standard \gls{iid} \gls{cscg} entries.
	We choose $\gamma_{\text{D}}=2.6$, $\gamma_{\text{F}}=2.4$, $\gamma_{\text{B}}=2$, and $\kappa_{\text{D}}=\kappa_{\text{F}}=\kappa_{\text{B}}=5$ for direct, forward and backward links.
	The finite decision threshold domain $\mathcal{T}$ is obtained by $b$-bit uniform discretization over the critical interval defined by the confidence bounds of edge hypotheses (i.e., lower bound of $\mathcal{H}_1$ and upper bound of $\mathcal{H}_L$) with confidence $1-\epsilon$, and we choose $b=9$ and $\epsilon=\num{e-3}$.
	All achievable rate points/regions are averaged over \num{1000} channel realizations.

@@

				I_{\text{B}}(x_{\mathcal{K}};\hat{y}^{\text{\gls{sr}}}) = K \log M - \frac{\iota}{M^K},

@@

			where $\iota \triangleq \sum_{m_{\mathcal{K}}} \mathbb{E}_{\hat{v}} \log \sum_{m_{\mathcal{K}}'} \exp ( - {\lvert x_{m_{\mathcal{K}}} - x_{m_{\mathcal{K}}'} + \hat{v} \rvert^2}/{2 \sigma^2} )$ and $\hat{v} \sim \mathcal{CN}(0,\sigma_v^2/N)$.
			% For a sufficiently large $N$, $\iota$ is negligible and the total backscatter rate approaches $K \log M$.

@@

		Fig.~\ref{fg:region_comparison} compares the typical achievable rate region/points of RIScatter and those applications.
		\emph{First,} we observe both \gls{bbc} and \gls{sr} almost ensure noise-free backscatter transmission when $N$ is sufficiently large.
		For \gls{bbc} with coherent energy detection, the conditional \gls{pdf} of accumulated receive energy \eqref{eq:energy_distribution_bbc} is more skewed at a large $N$, such that the equivalent \gls{dmtmac} \eqref{eq:dmtmac} becomes more reliable.
		For \gls{sr} with \gls{sic} and \gls{mrc}, the effective backscatter \gls{snr} is increased by $N$ times and the penalty term $\iota$ becomes insignificant.
		Such an \gls{sr} only guarantees the primary benefit with a large $N$, but decreases the backscatter symbol rate by a factor of $N$ and requires $N$ \gls{sic} processes to decode each backscatter symbol (tuple).
		\emph{Second,} the average primary rate slightly increases/decreases in the presence of a \gls{ambc}/\gls{ris} node, and the multipath benefit of \gls{sr} is unobvious.
		This is because the cascaded channel can be orders of magnitude weaker than the direct channel due to the double fading effect.
		\gls{ris} always ensures constructive superposition of direct and scattered components, while \gls{sr} only creates a quasi-static rich-scattering environment that stochastically enhances the average primary rate.
		When $N$ is moderate, the randomly scattered signals should be modelled as primary interference rather than multipath components, and the \gls{sr} point will move towards the \gls{ambc} point.
		\emph{Third,} RIScatter enables a flexible primary-backscatter tradeoff by smart input distribution design.
		In terms of maximum primary achievable rate, RIScatter coincides with \gls{ris} and outperforms the others by deterministic reflection pattern (no need for backscatter detection).
		On the other hand, for a large $N$, the maximum backscatter achievable rate of RIScatter is higher than \gls{ambc} but lower than \gls{bbc} and \gls{sr}.
		This is because both RIScatter and \gls{ambc} employ semi-coherent (instead of coherent) energy detection in the presence of primary uncertainty, and RIScatter with adaptive channel coding can achieve higher backscatter rate than \gls{ambc} with equiprobable inputs.
		Importantly, such a practical RIScatter detection is feasible for arbitrary $N$, and using a fast-switching node with smaller $N$ can increase the backscatter throughput per unit time while preserving the dynamic passive beamforming gain on the primary link.
	\end{subsection}
